---
title: "Choose a Good Title!"
author: "Put your name here!"
date: "put the date here"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)

```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
Red Dye Number 40  

S.W. Laagakos and F. Mosteller of Harvard University fed   mice different doses of red dye number 40 and recorded   the time of death in weeks. Results for female mice,   dosage and time of death are shown in the data  
 X1 = time of death for control group  
 X2 = time of death for group with low dosage  
 X3 = time of death for group with medium dosage  
 X4 = time of death for group with high dosage  
 Reference: Journal Natl. Cancer Inst., Vol. 66, p 197-212  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->
we saved the data to our r studio stuido project folder as a csv (comma seperated vale)file to our project folder. in the process we changed the variable names to control low medium and high representing how much red die they got. now we import the data.
```{r}
thedata <-read.csv("RedDie_data.csv",header=TRUE)
newdata <-stack(thedata)
newdata <-na.omit(newdata)
newdata2 <- gather(thedata,feed,deathtime,na.rm=TRUE)
```

#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
plot(values~ind,data=newdata)
```

```{r}
plot(deathtime ~ as.factor(feed),data=newdata2)
```

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
favstats(deathtime ~ as.factor(feed),data=newdata2)
```
## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
```{r}
model1 <- aov(deathtime ~ as.factor(feed),data=newdata2)
summary.aov(model1)
```
```{r}
#we specify the margins starting at the bottom and proceeding clockwise - thus 8.7 is the left side margin to hold the names of the factors
par(mar = c(3, 5.7, 2, 2))
plot(TukeyHSD(model1),las=2)
```

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
